---
title: "TrueBlocks Chifra | Correlation Investigation"
author: "Matthieu Fournier"
date: "2022-08-22"
output:
  html_document:
    df_print: paged
---

# Data Prep
```{r}
nosis <- read.csv("gnosis-step-50000.csv")
nosis <- subset(nosis, select = -c(finalized))
head(nosis)
mn <- read.csv("mainnet-step-50000.csv")
mn <- subset(mn, select = -c(finalized))
head(mn)
sep <- read.csv("sepolia-step-5000.csv")
sep <- subset(sep, select = -c(finalized))
head(sep)
pairs(nosis)
pairs(mn)
pairs(sep)

mn_nofee <- mn[1:260,]
mn_fee <- mn[261:308,]
View(mn_nofee)
```







# Using Visuals to find Correlations: MainNet

## Main Net (Before Split)
```{r}

pairs(mn)
par(mfrow=c(2,2))
plot(mn$miner, mn$gasLimit)
plot(mn$miner, mn$gasUsed)
plot(mn$timestamp, mn$gasLimit)
plot(mn$timestamp, mn$miner)
mnN <- sum(unique(mn$miner))
nosisN <- sum(unique(nosis$miner))
sepN <- sum(unique(sep$miner))
#bargraph: hist(mnN, nosisN, sepN)
```
### time vs. diff
```{r}
plot(mn$timestamp, mn$difficulty)
#polynomial best fit
poly.diff <- lm(difficulty ~ poly(timestamp, 6), data = mn)
summary(poly.diff)
#plot line of fit
lines(mn$timestamp, predict(poly.diff), col='red')
#predict effectively, when timestamp exceeds 1.5 billion seconds
presplit.diff <- as.data.frame(predict(poly.diff))
```


```{r}
plot(mn$timestamp, mn$transactionsCnt)
poly.transCnt <- lm(transactionsCnt ~ gasUsed, data = mn)
summary(poly.transCnt)
lines(mn$timestamp, predict(poly.transCnt), col="red")

```

## Main Net, No Base Fee

### time vs. diff

```{r}

plot(mn_nofee$timestamp, mn_nofee$difficulty)
#polynomial best fit
poly.diff2 <- lm(difficulty ~ poly(timestamp, 6), data = mn_nofee)
summary(poly.diff2)
#plot line of fit
lines(mn_nofee$timestamp, predict(poly.diff2), col='orange')
#predict effectively, when timestamp exceeds 1.5 billion seconds
no.fee.diff <- as.data.frame(predict(poly.diff2))
```

### gasUsed and time vs. transactionsCnt

```{r}
#Heavy noise. 64% predictability
plot(mn_nofee$timestamp, mn_nofee$transactionsCnt)
poly.transCnt2 <- lm(transactionsCnt ~ gasUsed, data = mn_nofee)
summary(poly.transCnt2)
lines(mn_nofee$timestamp, predict(poly.transCnt2), col="red")
```


```{r}
pairs(mn_nofee)
lm.mn_nf <- lm(gasUsed ~ timestamp, data = mn_nofee)
lm.mn_nf <- lm(gasLimit ~ timestamp, data = mn_nofee)

lm.mn_nf <- lm(hash ~ difficulty, data = mn_nofee)
summary(lm.mn_nf)
```





## With basefees, Main Net
```{r}
#pairs(mn_fee)
plot(mn_fee$gasUsed, mn_fee$miner)
lm.mnf <- lm(gasLimit ~ miner, data = mn_fee)
summary(lm.mnf)
```


```{r}
plot(mn_fee$timestamp, mn_fee$difficulty)
#polynomial best fit
poly.diff3 <- lm(difficulty ~ poly(timestamp, 3), data = mn_fee)
summary(poly.diff3)
#plot line of fit
lines(mn_fee$timestamp, predict(poly.diff3), col='cyan')
#predict effectively, when timestamp exceeds 1.5 billion seconds
fee.diff <- as.data.frame(predict(poly.diff3))
```

# Using Visuals to find Correlations: Gnosis
```{r}
require(dplyr)
unique(nosis$miner)
par(mfrow=c(2,2))
plot(nosis$miner, nosis$gasLimit)
plot(nosis$miner, nosis$gasUsed)
plot(nosis$timestamp, nosis$gasLimit)
plot(nosis$timestamp, nosis$miner)


```


# Using Visuals to find Correlations: Sepolia
```{r}
pairs(sep)
par(mfrow=c(2,2))
plot(sep$miner, sep$gasLimit)
plot(sep$miner, sep$gasUsed)
plot(sep$timestamp, sep$gasLimit)
plot(sep$timestamp, sep$miner)
unique(sep$miner)

```

# Testing Model Predictive Accuracy and Noise

```{r}
library(dplyr)
PRESS <- function(linear.model) {
  #' calculate the predictive residuals
  pr <- residuals(linear.model)/(1-lm.influence(linear.model)$hat)
  #' calculate the PRESS
  PRESS <- sum(pr^2)
  
  return(PRESS)
}

pred_r_squared <- function(linear.model) {
  #' Use anova() to get the sum of squares for the linear model
  lm.anova <- anova(linear.model)
  #' Calculate the total sum of squares
  tss <- sum(lm.anova$'Sum Sq')
  # Calculate the predictive R^2
  pred.r.squared <- 1-PRESS(linear.model)/(tss)
  
  return(pred.r.squared)
}
pred_r_squared(poly.diff)
pred_r_squared(poly.diff2)
pred_r_squared(poly.diff3)
pred_r_squared(poly.transCnt)
pred_r_squared(poly.transCnt2)



```


## Further work: Order miners by timestamp, ei first to ethereum graph that as underlay with miner and gasUsed, tranCNT or difficulty.

## Pie chart, with categories

## Color code scatter plot by miner