---
title: "R Tutorial"
author: "Matthieu Fournier"
date: "2022-08-17"
output:
  html_document:
    df_print: paged
---

# Formatting: RStudio

1. This is R Markdown or RMD. It is the most effective way to write analysis and code together to produce a beautiful report.

```{r}    #creates the beggining of a code chunk

```       #ends the code chunk, when uniterupted it looks like this


2. The number of hashtags before a line determine the text size, one gives title, three gives subtitle.


3. Other formatting tricks in the original project file. (par(mfrow(2,2))

## Titles are found outside the chunk
```{r}
#I cannot give a title in here, only comments for code with a hashtag

Data.Frame.TrueBlocks <- read.csv("mainnet.csv")  #Import the csv into R, we now have a data frame

Data.Frame.TrueBlocks$New.Var <- c(1:3028) #Before the arrow is creating a new column in the data frame. After is giving it the values of a vector 1-3028 given because thats the number of columns
print(NROW(Data.Frame.TrueBlocks))  #Function NROW counts the rows in a data frame and print gives the display below when the chunk is ran, green arrow up there. 
 
```

# Data Frames: RStudio

## Basic Tutorial Package
```{r}
#install.packages(swirl)   #Basic code to install packages. I prefer doing this through the packages portal in my bottom right corner
library(swirl)  #library and the package being used is a beneficial line of to ensure the package is installed and running in this code chunk
#swirl()
```

# Helpful Packages: RStudio

### Data Cleaning
- Tidyr - Tidyverse - dplyr

### Graphing Visualizing
- ggplot2 and base r
- rpartplot for tree regression

### Data Sets
- MASS, mtcars, ISLR

### Mining and Modeling
- glmnet, rstan, randomforest, AER

# Think like a statistician
- I am curious with numbers, ie "if try to run this against that will I get anything out the ordinary"
- I love to look at all the variables and just think of weird connections that could be correlations or even sometimes causation.
- The models and programs will prove the results your looking for if they're there. It's our job not to let our  bias get in the way. You can look at data set with any underlying assumption of why something happens but it won't always be the true case of causation. In data science we need to push ourselves to consider every angle, so get curious...