---
title: "Exploring Ethereum Foundation Tip Jar Data"
author: "Ed Mazurek"
date: "3/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('etherTip.init.R')
```

- replaced known contract addresses with readable string
- parsed out the function calls into `fn.name` and `args[0:10]` (needs work).

Makes the data a lot more readable:

```{r}
etherTip.fns %>%
  filter(is.fn.call, have.abi) %>%
  select(from, to, fn.name) %>% print(n = 10, width = Inf)
```

## Visualizations

### Frequency of function calls

```{r message=FALSE}
etherTip.fns %>%
  filter(have.abi) %>%
  ggplot(aes(x = datesh, fill = fn.name)) + 
  geom_histogram()
```

### Frequency of function calls but easier to see

- Much easier to identify where proposals are happening, ownership transfer, etc.

```{r message=FALSE, fig.height = 8, fig.width = 11}
etherTip.fns %>%
  filter(have.abi) %>%
  ggplot(aes(x = datesh, fill = fn.name)) + 
  facet_wrap(facets= 'fn.name') +
  labs(title = 'Function call count') + 
  geom_histogram()
```


### functions on unicorn token vs foundation tip jar contract

- filtered on transactions with either the unicorn token OR foundation tip jar in the "to" field.
- makes me think we should be treating these contracts separately (I think you mentioned the same thing)

```{r message=FALSE}
etherTip.fns %>%
  filter(have.abi) %>%
  filter(to %in% names(special.addr)) %>%
  ggplot(aes(x = datesh, fill = fn.name)) +
  facet_wrap('to', nrow = 2) +
  geom_histogram()
```

### other possibilities

- unicorn tokens still owned by original owner
- cumulative sum of all ether transferred into the tip jar contract
- (a lot more)