---
title: "Exploring RChain Token (RHOC) Data"
author: "Ed Mazurek"
date: "3/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('rchain.init.R')
```

- replaced known contract addresses with readable string
- parsed out the function calls into `fn.name` and `args[0:10]` (needs work).

Tried parsing out "known addresses." Makes it easier to reason about.

```{r}
rchain.fns %>%
  filter(is.fn.call, have.abi) %>%
  select(from, to, fn.name) %>% print(n = 10, width = Inf)
```

## Visualizations

### Frequency of function calls

```{r message=FALSE}
rchain.fns %>%
  filter(have.abi) %>%
  ggplot(aes(x = datesh, fill = fn.name)) + 
  geom_histogram()
```

### Frequency of function calls but easier to see

- confirm, execute coming from multisig?

```{r message=FALSE, fig.height = 8, fig.width = 11}
rchain.fns %>%
  filter(have.abi) %>%
  ggplot(aes(x = datesh, fill = fn.name)) + 
  facet_wrap(facets= 'fn.name') +
  labs(title = 'Function call count') + 
  geom_histogram()
```


### functions on contracts

- includes any other contracts in the data set that I've named. So far, only named a multisig that seemed to be doing airdrops.

```{r message=FALSE}
rchain.fns %>%
  filter(have.abi) %>%
  filter(to %in% names(special.addr)) %>%
  ggplot(aes(x = datesh, fill = fn.name)) +
  facet_wrap('to', nrow = 2) +
  geom_histogram()
```

### other possibilities

- price and transfer volume: at what price was RChain at in Jan 2018? Why so much transfer volume around then?